%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Scientist} % Job title
    {Betclic Group} % Organization
    {Bordeaux, France} % Location
    {Jun. 2019 - current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Sport betting and casino personalization/recommender system (hybrid recommendations approaches).}
        \item {Anti Money Laundering detection (ACAMS Certified Anti-money Laundering Specialist).}
        \item {Safer gaming and addiction behavior detection (classification and time series).}
        \item {Lifetime value prediction (survival analysis).}
      \end{cvitems}
    \vspace{9} 
    Using : Python (Pandas, Scikit-learn, Pytorch, Tensorflow/Keras, Shap, Pytest), Apache Airflow, AWS Sagemaker, Snowflake.
    }

%---------------------------------------------------------
  \cventry
    {Data Scientist Advisor} % Job title
    {Cdiscount} % Organization
    {Bordeaux, France} % Location
    {Nov. 2018 - Mai. 2019} % Date(s)
    {
       \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Massive customer clustering.}
        \item {Bot detection (pattern analysis).}
        \item {Sentiment analysis (Natural Langage Processing).}
        \item {Object detection in picture (Mask-RCNN, MSCOCO dataset).}
      \end{cvitems}
      \vspace{9} 
    Using : Python (Scikit-learn, Numpy, Pandas, Scipy, Shap, Luigi), SQL, Apache Hadoop Hive.
    }

%---------------------------------------------------------
  \cventry
    {Data Scientist} % Job title
    {} % Organization
    {} % Location
    {Oct. 2016 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Search engine relevance.}
        \item {Products recommendation engine.}
        \item {Algorithms evaluation (A/B testing).}
        \item {Focus on website's KPI improvment.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Scientist Intern} % Job title
    {} % Organization
    {} % Location
    {Mar. 2016 - Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Marketing targeting : behavioral analysis and improvment of the search engine relevance through AB test, proof of concept personnalisation client (classification and clustering).}
        \item {Geographical data : Purchase forecasting by geographic zone.}
        \item {Statistical analysis : data enrichment with INSEE database, implementation and developement of geocoding tool.}
        \item {Intern innovation contest : Setting of a new operationnal service for the client, forcasting system of product storage to allow express delivery.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Scientist Intern} % Job title
    {Idaia Group} % Organization
    {Bordeaux, France} % Location
    {Jun. 2015 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Sourcing, implementation and development of machine learning tools (mainly multiclass classification) in Python and Scala into Apache Spark large-scale data framework.}
      \end{cvitems}
      \vspace{9} 
      Using : Python (Scikit-learn, Numpy, Scipy, NLTK), Scala, Spark (MLlib).
    }
    
%---------------------------------------------------------
\end{cventries}
