%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Recommandations (en anglais)}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

\cventry
    {Chief Data Officer} % Degree
    {Iouri Chapochnikov} % Institution
    {Betclic} % Location
    {} % Date(s)
    {
    \begin{cvitems}
    I had the pleasure of working with Thomas on several data science projects, and I wholeheartedly recommend him. His expertise in machine learning, statistics, and mathematics is exceptional, and he consistently delivered results with projects that went into production, including high complexity, high load recommendations systems. Thomas has a unique talent for simplifying complex data science concepts, making him an excellent presenter who can effectively communicate these ideas to others. Beyond his professional skills, Thomas is a very pleasant and dedicated individual, often going above and beyond, even working on weekends. It's a pleasure to have him in my team.
\end{cvitems}
    }
    
%---------------------------------------------------------

  \cventry
    {Head of data Science} % Degree
    {Bertrand Beaufils} % Institution
    {Betclic} % Location
    {} % Date(s)
    {
    \begin{cvitems}
    In addition to being technically excellent, Thomas is a very nice person.
    As Head of Data Science, I saw very quickly within Betclic the importance of having him in the team.
    Within two squads, he is the Data Science referent and facilitates communication/interactions between the stakeholders.
    Always curious and proactive, he manages to solve data science challenges to production, while always being available to support the development of team members' skills.
    Any employee/manager would be happy to work with Thomas, and not just because he brings great croissants to the office!
    \end{cvitems}
    }

%---------------------------------------------------------

\cventry
    {Head of Data} % Degree
    {Bertrand Warot} % Institution
    {Ejara, ex-Betclic Data Manager} % Location
    {} % Date(s)
    {
    \begin{cvitems}
    Thomas is a gem!
I have had the pleasure to manage and work with him on several projects.
His a fast learner and adapted quickly to the specificities of our industry. His deep scientific knowledge along with his coding skills are his strongest assets (and two of the most important skills for a data scientist). I also have been amazed by the creative approaches he has to rather common issues, always willing to test new ideas, which paid most of the time.
He is definitely passionate about Data Science and Mathematics, and loves to share his knowledge and make it accessible to everyone.
I would be glad to have the occasion to work with him again in the future!
    \end{cvitems}
    }

%---------------------------------------------------------


\end{cventries}
