%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Scientist} % Job title
    {Betclic Group} % Organization
    {Bordeaux, France} % Location
    {Jun. 2019 - current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Anti Money Laundering detection.}
        \item {Responsible gambling (addiction behavior) detection.}
        \item {Personalized offers for emailing campaign.}
        \item {Lifetime value prediction.}
      \end{cvitems}
    \vspace{9} 
    Using : Pandas, Scikit-learn, Pytorch, Tensorflow2/Keras, Shap, Airflow, AWS, Unittest/Pytest, Great Expectation...  
    }

%---------------------------------------------------------
  \cventry
    {Data Sientist Advisor} % Job title
    {Cdiscount} % Organization
    {Bordeaux, France} % Location
    {Nov. 2018 - Mai. 2019} % Date(s)
    {
       \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Massive customer clustering.}
        \item {Bot detection (pattern analysis).}
        \item {Sentiment analysis (Natural Langage Processing).}
        \item {Object detection in picture (Mask-RCNN, COCO dataset).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Sientist} % Job title
    {Cdiscount} % Organization
    {Bordeaux, France} % Location
    {Oct. 2016 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Search engine relevance.}
        \item {Recommendation engine.}
        \item {Algorithms evaluation (A/B testing).}
        \item {Focus on website's KPI improvment.}
        \item {Python development (Scikit-learn, Numpy, Pandas, Scipy, Luigi etc).}
        \item {Hadoop Hive \& SQL Databases.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Sientist Intern} % Job title
    {Cdiscount} % Organization
    {Bordeaux, France} % Location
    {Mar. 2016 - Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Marketing targeting : behavioral analysis and improvment of the search engine relevence through AB test, proof of concept personnalisation client (classification and clustering).}
        \item {Geographical data : Purchase forecasting by geographic zone.}
        \item {Statistical analysis : data enrichment with INSEE database, implementation and developement of geocoding tool.}
        \item {Intern innovation contest : Setting of a new operationnal service for the client, forcasting system of product storage to allow express delivery.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Sientist Intern} % Job title
    {Idaia Group} % Organization
    {Bordeaux, France} % Location
    {Jun. 2015 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Sourcing, implementation and development of machine learning tools (mainly multiclass classification) in Python and Scala into Apache Spark large-scale data framework.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\end{cventries}
